Reconstructing Rearrangement Phylogenies of Natural Genomes

### 2023-10-20 docs/manuscript/main.tex
committing intermediate state

\begin{document}
%
\title{\todoDany{Approve or change: } Reconstructing Rearrangement Phylogenies}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA \and
Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
\email{lncs@springer.com}\\
\url{http://www.springer.com/gp/computer-science/lncs} \and
ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
\email{\{abc,lncs\}@uni-heidelberg.de}}
%
\maketitle              % typeset the header of the contribution
%
\todo{Authors and order? $\rightarrow$ until Oct 23rd.}
\begin{abstract}
\todo{We have to submit this until Oct 23rd.}

>>>>

\begin{document}
%
\title{Reconstructing Rearrangement Phylogenies of Natural Genomes}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Leonard Bohnen\"amper\inst{1}\orcidID{0000-0003-4508-0078} \and
    Jens Stoye \inst{1}\orcidID{0000-0002-4656-7155} \and
    Daniel D\"orr \inst{2}\orcidID{0000-0002-3720-6227}
}
%
\authorrunning{L. Bohnenk\"amper et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Technology and Center for Biotechnology (CeBiTec), Bielefeld University, Germany\\ 
    \email{lbohnenkaemper@techfak.uni-bielefeld.de}, \email{stoye@techfak.uni-bielefeld.de}\\
\and
Institute for Medical Biometry and Bioinformatics, Medical Faculty, and Center for Digital Medicine, Heinrich Heine University, Germany\\
\email{daniel.doerr@hhu.de}}

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
    We study the classic problem of inferring ancestral genomes on a given phylogeny and a given set of extant genomes, also known as \emph{small parsimony problem} (SPP). 
    More specifically, we address a scenario where genomes represent sets of linear or circular successions of oriented genomic markers orders, also known as \emph{gene orders} that evolve along the branches of the phylogeny and are altered by a general evolutionary model that supports a genome rearrangements emulated through the double-cut-and-join (DCJ) operation and by segmental insertions and deletions.

    Even under simple evolutionary models, this problem is computationally intractable,
